---
title: "Exercise 2"
author: "Mia Simmons"
date: "2024-11-28"
output: github_document
---

# Introduction

Welcome to Exercise 2! Here, we will make a function that will convert words into the brand new Cat Latin cipher. In Cat Latin, the last letter of a word is moved to the front, the word is repeated, and the end of the word has "-meow" added to it.

---

# Coding

## Setup

```{r setup}

library(dplyr)
library(tidyverse)
library(stringr)
library(testthat)

```

## Function

```{r create function}
#' Convert words into Cat Latin
#'
#' @description
#'Moves the last letter of a word to the front and adds "-meow" to the end of it. Can be applied to lists of words, and is only applicable to character vectors.
#'
#' @param x The character vector or list of vectors to be used.
#'
#' @return A character vector
#' @export
#'
#' @examples
#' cat_latin("cat")

cat_latin <- function(x) { 
  
  # This stops the function if the input is of the incorrect type
  
  if(!is.character(x)) { 
    stop("Sorry, this function only works on character vectors") 
  }
  
  # This converts the input into Cat Latin by re-arranging the components
  
   str_c(str_sub(x, -1), str_sub(x, end = -2), x, "-meow")
}

```

## Examples

```{r one word}

# Convert a one word string to Cat Latin

cat_latin("cat")

```

```{r multiple words}

# Apply Cat Latin to multiple words

y <- c("cat", "dog")

cat_latin(y)

```

## Tests

```{r}

# Test 1 - Non-character inputs result in an error

test_that("Non-character input error", {
  expect_error(cat_latin(15))
})

```

```{r visible result}

# Test 2 - The function prints the result to the console

test_that("Print result", {
  expect_visible(cat_latin("Hello"))
})

```

```{r expected class}

# Test 3 - Output is the expected class

test_that("Expect output to be a character vector", {
  expect_type(cat_latin("Hello"), "character")
})

```

---

# Conclusion

In conclusion, this Exercise shows the development of the function *cat_latin*, which converts words into the newly developed Cat Latin Cipher. Two examples were shown, and three tests run to show that the function works properly.
